\documentclass [12pt,letterpaper]{report}

% Standard packages
\usepackage{amsmath}		% Extra math definitions
\usepackage{graphics}		% PostScript figures
\usepackage{setspace}		% 1.5 spacing
\usepackage{longtable}          % Tables spanning pages
\DeclareGraphicsExtensions{.pdf,.png,.jpg,.mps}
\usepackage{amssymb}
\usepackage{courier}
\usepackage{mathtools}
\usepackage{ amsmath, bm }
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{yhmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{dsfont}
\usepackage{bbm}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage[english, frenchb]{babel}
\usepackage[T1]{fontenc}
\usepackage[section]{placeins}


% Custom packages
%\usepackage[first]{datestamp}	% Datestamp on first page of each chapter
\usepackage[fancyhdr]{McECEThesis}	% Thesis style
\usepackage{McGillLogo}		% McGill University crest

% $Id: ThesisEx.tex,v 1.1 2005/06/09 12:48:46 kabal Exp $

\usepackage{color}
\def\headrulehook{\color{red}}		% Color the header rule

%===== page layout
% Define the side margins for a right-side page
\insidemargin = 1.3in
\outsidemargin = 0.8in

% Above margin is space above the header
% Below margin is space below footer
\abovemargin = 1.1in
\belowmargin = 0.75in  %0.75in

\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\newcommand\bigfrown[2][\textstyle]{\ensuremath{%
  \array[b]{c}\text{\scalebox{2}{$#1\frown$}}\\[-1.3ex]#1#2\endarray}}

%========= Document start

\begin {document}

%===== Title page
\nopagebreak[4]
\title{The Extended Neyman-Pearson Hypotheses Testing Framework and its Application to Spectrum Sensing in Cognitive Wireless Communication}
\author{An Jiang}
\date{\Month\ \number\year}
\organization{%
%  \\[0.2in]
  \McGillCrest{!}{1in}\\	% McGill University crest
%  \\[0.1in]
  Department of Electrical \& Computer Engineering\\
  McGill University\\
  Montreal, Canada}

\note{%
  {\color{red} \hrule height 0.4ex}
  \vskip 1ex
  A thesis submitted to McGill University in partial fulfillment of the
  requirements for the degree of Master of Engineering (M.Eng) in Electrical Engineering.
  \vskip 1ex
  \copyright\ \the\year\ An Jiang
}

  \pagebreak[2]
\maketitle

%===== Justification, spacing for the main text
\raggedbottom
%\onehalfspacing
\doublespacing
\pagenumbering{roman}

%===== Abstract, Sommaire & Acknowledgments
\section*{\centering Abstract}
We propose a Modified Extended Neyman Pearson (MENP) framework which is suitable for spectrum sensing when there might be different types of primary signals. Our work generalizes the existing Neyman Pearson (NP) test to accommodate multiple probabilities of false alarm constraints. This allows the cognitive radio wireless communication system to provide different levels of protection for various primary users.  
The M-ROC surface, representing the relationship between the probability of detection and the constraints, is used to depict the performance of MENP testing.   

Using the MENP framework, energy and cyclostationary based spectrum detector are developed for sensing a free channel in the presence of multiple primary signals. 
These detectors are designed to have the largest probability of detecting a free channel under any probability of false alarm constraints.  
Performance analysis results  for both detectors are presented.  
\newpage

\selectlanguage{frenchb}
\section*{\centering Sommaire}
Nous proposons un nouveau modèle au nom de Modèle Neyman Pearon Modifié (MNPM) qui nous permettra de détecter les signaux sensoriels dans le cas où des signaux principaux sont présents. Ce modèle utilise le test de Neyman Pearon (NP) dans le but de réduire les probabilités de fausses alarmes causées par l'interférence des signaux principaux. Notre modèle permet au système de communication sans-fil des radios cognitives de fournir plusieurs couches de protection à leurs utilisateurs. La surface M-ROC, représentant le lien entre la probabilité de détection et les restrictions qui proviennent des fausses alarmes, est utilisé pour afficher nos résultats du test de MNPM.

Nous utilisons le modèle MNPM pour développer les détecteurs de spectre d'énergie et les détecteurs cyclostationnaires peuvent capturer efficacement des bandes de fréquences libres sous la présence des signaux principaux. Ces détecteurs sont conçus pour avoir une plus grande possibilité de détecter les bandes de fréquences libres sous la restrictions des fausses alarmes.
Les analyses de la performance du détecteur de spectre d'énergie et du détecteur cyclostationnaire seront présentées ci-dessous.

\newpage
\selectlanguage{english}
\section*{\centering Acknowledgments}

I would like to thank my supervisor Prof. Harry Leib for his guidance throughout my studies and providing me with financial support. I am also very grateful to my former and current members of my lab. They provided me a lot of help to adapt the life in Montreal. Finally,  I would like to thank my grandparents for their encouragement throughout my study. 
%========== Tables of contents, figures, tables
\tableofcontents
\listoffigures
\listoftables

\newpage
\chapter*{List of Acronyms}\markright{List of Terms}

\begin{longtable}{ll}
  AWGN    &   Additive White Gaussian Noise\\
  CDMA    &   Code Division Multiple Access\\
  CP      &   Cyclic Prefix\\
  ENP     &   Extended Neyman Pearson\\
  MENP    &   Modified Extended Neyman Pearson\\
  MROC    &   Modified Receiver Operating Characteristic\\
  OFDM    &   Orthogonal Frequency Division Multiplexing\\
  QPSK    &   Quadrature Phase-Shift Keying         \\
  ROC     &   Receiver Operating Characteristic
\end{longtable}

\cleardoublepage
\pagenumbering{arabic}

%========== Chapters
\typeout{}
\include{Intro/Introduction}

%========== Chapter 2
\typeout{}
\include{2/2}

%==========
\typeout{}
\include{3/3}

%==========
\typeout{}
\include{4/4}

%= = = = 
\typeout{}
\include{5/5}
%==========
\typeout{}
\include{conclu/con}

%========== Appendices
\appendix

%==========
\typeout{}
\input{A-A}

%========== Bibliography
\typeout{}
\begin{singlespace}
  \bibliography{ThesisEx}
  \bibliographystyle{ieeetr}
\end{singlespace}

\end{document}
